Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-29 supp/supp.qmd
Move stuff around and add some supp updates

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)

@@

 ##### ADDED BY ML"  
install.packages("gender")
install.packages("genderdata")
library(gender)

## testing - delete thi later
#gender(c("Madison", "Hillary"), years = 2000, method = "ssa")
#gender(c("Madison", "Hillary"), method = "genderize") #works ok until limit of 100 is reached
#gender(data3$submitting_author_firstname, method = "genderize") #works ok until limit of 100 is reached

@@

data3 %>% 
  filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>% 
  write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot)

@@

 ##### ADDED BY ML"  
## testing - delhi later
#gender(c("Madison", "Hillary"), years = 2000, method = "ssa")
#gender(c("Madison", "Hillary"), method = "genderize") #works ok until limit of 100 is reached
#gender(data3$submitting_author_firstname, method = "genderize") #works ok until limit of 100 is reached

@@

#data3 %>% 
  #filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>% 
 # write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv
